Fig5

### 2020-03-06 analysis/figure5-maniptsne.Rmd
now with tsne fig 5

  df <- df %>% mutate(hiloPRL = fct_collapse(treatment, 
                                  lo = c("m.inc.d8", "m.inc.d3", "m.inc.d9", "inc.d3", "inc.d9", "lay"),
                                  hi = c("inc.d17",   "m.inc.d17", "prolong" ,  "hatch"  ,   "m.n2", "extend", "n5")),
                extint = fct_collapse(treatment, 
                                  eggs = c("inc.d3", "inc.d9", "inc.d17", "prolong", "lay"),
                                  chicks = c( "m.inc.d8", "hatch", "extend", "n5"),
                                  loss = c("m.inc.d3", "m.inc.d9", "m.n2", "m.inc.d17")))
  df$extint <- factor(df$extint, levels = levelsextint)
  return(df)
}

@@

expdesign2 <- png::readPNG("../figures/images/DoveParentsRNAseq_hypothesis.png")
expdesign2 <- ggdraw() +  draw_image(expdesign2, scale = 1)

@@

fig6 <- plot_grid(expdesign2, bcdhijefg, nrow = 2, labels = c("e"), label_size = 8, rel_heights = c(0.4,1))
fig6

>>>>

  df <- df %>% mutate(hiloPRL = fct_collapse(treatment, 
                                  lo = c("m.inc.d8", "m.inc.d3", "m.inc.d9", "inc.d3", "inc.d9", "lay", "bldg"),
                                  hi = c("inc.d17",   "m.inc.d17", "prolong" ,  "hatch" ,  "m.n2", "extend", "n5")),
                extint = fct_collapse(treatment, 
                                  eggs = c("inc.d3", "inc.d9", "inc.d17", "prolong", "lay"),
                                  chicks = c( "m.inc.d8", "hatch", "extend", "n5"),
                                  loss = c("m.inc.d3", "m.inc.d9", "m.n2", "m.inc.d17", "bldg")))
  df$extint <- factor(df$extint, levels = levelsextint)
  return(df)
}

@@

expdesign2 <- png::readPNG("../figures/images/DoveParentsRNAseq_maniptsne.png")
expdesign2 <- ggdraw() +  draw_image(expdesign2, scale = 1)

@@

fig6 <- plot_grid(expdesign2, bcdhijefg, nrow = 2, labels = c("e"), label_size = 8, rel_heights = c(0.5,1))
fig6
